Fluent statistical computing interfaces for biological data analysis

### 2020-07-24 Rmd/01-intro.Rmd
typo spotting and reference adds

In the final chapter, we move away from data wrangling and towards the 
integration of visualisation with model-based summaries of high-dimensional
data sets. We focus on a common tool for EDA (especially applied to single-cell
transcriptomics): non-linear dimension reduction (NLDR). We consider the incorporation of 
interactive and dynamic graphics to assist analysts in using NLDR techniques
for cluster orientation tasks. In particular, we advocate for the use of tours
[@Cook1995-bi] alongside an NLDR visualisation to highlight potential pitfalls 
and distortions of obtained from an NLDR method. This approach acknowledges that
there is no 'one' best visualisation or dimension reduction for a 
high-dimensional dataset, and we often want to have an understanding of both the global and local structure within our data.

Chapter \@ref(ch:tsne) introduces a software package called *liminal* for 
constructing these views and a user interaction framework for identifying 
distortions. We present several case studies using data sets from both 
single-cell transcriptomics and  machine learning  for using our approach to diagnose the quality of  results obtained via popular NLDR methods
like t-distributed stochastic neighbour embeddings (t-SNE).

>>>>

In the final chapter, we move away from data wrangling and towards the 
integration of visualisation with model-based summaries of high-dimensional
data sets. We focus on a common tool for EDA (especially applied to single-cell
transcriptomics): non-linear dimension reduction (NLDR). We consider the incorporation of 
interactive and dynamic graphics to assist analysts in using NLDR techniques
for cluster orientation tasks. In particular, we advocate for the use of tours
[@Cook1995-bi] alongside an NLDR visualisation to highlight potential pitfalls 
and distortions obtained from an NLDR method. This approach acknowledges that
there is no 'one' best visualisation or dimension reduction for a 
high-dimensional dataset, and we often want to have an understanding of both the global and local structure within our data.

Chapter \@ref(ch:tsne) introduces a software package called *liminal* for 
constructing these views and a user interaction framework for identifying 
distortions. We present several case studies using data sets  both 
single-cell transcriptomics and  machine learning  for using our approach to diagnose the quality   results obtained via popular NLDR methods
like t-distributed stochastic neighbour embeddings (t-SNE) [@Maaten2008-sk].
